---
title: "Ties detailed table"
author: ""
date: "2020-06-07"
slug: tie-detailed-table
page-layout: full
categories:
  - Ties
format:
  html:
    css: "../../styles.css"
---


```{r setup, echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(tidyverse)
library(DT)

source(here::here("shared_code/tie_functions.R"))
source(here::here("shared_code/tie_config.R"))

```

The table below contains all the input columns used in the ["Difficulty" calculation](/posts/tie-difficulty-calculation/index.qmd). In order for the table to be interactive (searchable and able to be re-ordered), the ability to click (or tap) the image to enlarge has been sacrificed.


```{r, echo=FALSE}
ties_detailed_tbl %>%
  # FORCE FIX: Look at the image column and rewrite the HTML tags to be small
  mutate(image = gsub("<img src", "<img width='120' src", image)) %>% 
  mutate(overall_difficulty = as.character(overall_difficulty)) %>% 
  datatable(escape = FALSE, 
            options = list(
              autowidth = TRUE, 
              pageLength = nrow(ties_data)
            ),
            rownames = FALSE,
            colnames = c('Name', 'Difficulty', 'Shaping', 'No. Ties', 'No. steps', 'No. loops', 'Fold in half', 'End tied', 'Image')
            )
```



<br><br>

<p style="text-align: center; margin-top: 2rem; font-size: 0.85rem; font-weight: 500; color: gray;">
  This page has been read <span id="goat-count" style="font-weight: bold; color: currentColor;">...</span> times.
</p>

<script>
  (function() {
    let path = window.location.pathname;

    // Strip trailing slashes to accurately match your "postfolder.json" format
    if (path.length > 1 && path.endsWith('/')) {
      path = path.slice(0, -1);
    }

    const targetUrl = 'https://bengin.goatcounter.com/counter//' + path + '.json';

    fetch(targetUrl)
      .then(response => {
        // If it's a 404 error, GoatCounter is saying "This page has 0 historical views"
        if (response.status === 404) {
          return { count: 0 }; 
        }
        // Catch actual fatal server network drops
        if (!response.ok) {
          throw new Error('API or CORS issue');
        }
        return response.json();
      })
      .then(data => {
        // Seamless pluralization checker for perfect grammar
        let count = data.count;
        document.getElementById('goat-count').innerText = count;
      })
      .catch(err => {
        // Only falls back to "a few" if an adblocker blocks the connection completely
        document.getElementById('goat-count').innerText = "a few";
      });
  })();
</script>
